Interval Probability for Fuzzy Quantum Theories

### 2016-06-17 prob.tex
"Referenece\M. Born, On the Quantum Mechanics of Collisions.pdf" Added...
Change a little bit...

In the remainder of the paper, we consider variations of quantum
probability spaces motivated by computation of numerical quantities in
a world with limited resources:
\begin{itemize}
\item Instead of the Hilbert space $\Hilb$ (constructed over the
  uncountable and uncomputable complex numbers $\mathbb{C}$), we will
  consider variants constructed over finite
  fields~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013}.
\item Instead of real-valued probability measures producing results in
  the uncountable and uncomputable interval $[0,1]$, we will consider
  finite set-valued probability measures~\cite{Artstein1972,PuriRalescu1983}.
\end{itemize}
We will then ask if it is possible to construct variants of quantum
probability spaces under these conditions. The main question is
related to the definition of probability measures: is it possible to
still define a probability measure as a function that depends on a
single state? Specifically,
\begin{itemize}
\item given a state $\ket{\psi}$, is there a probability measure
  mapping events to probabilities that only depends on $\ket{\psi}$?
  In the conventional quantum probability space, the answer is yes by
  the Born rule~\cite{Born1983,Mermin2007} and the map is given by:
  $E \mapsto \ip{\psi}{E\psi}$.
\item given a probability measure $\mu$
  mapping each event $E$
  to a probability, is there a \emph{unique} state $\psi$
  such that $\mu(E)
  =
  \ip{\psi}{E\psi}$? In the conventional case, the answer is yes by
  Gleason's
  theorem~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
\end{itemize}

@@

\item A set of mutually orthogonal projections $P_{i}$ is called an ideal
measurement if it is a partition of the identity, i.e., $\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$. 

@@

\yutsung{About continuity, one of the confusion comes from the subtle
correspondence between the measurement processes and observables.
Consider the following observables and their measurement processes:
\begin{itemize}
\item For any $x\in\R$, consider the observable operator~$\mathbf{O}_{x}=\proj{1}+x\proj{-1}$.
Except $x=1$, given the system in the state~$\ket{\phi}$, we can
denote the measurement process for $\mathbf{O}_{x}$ by ${\cal O}_{x}$:
\begin{enumerate}
\item With probability~$\mu_{\phi}\left(\proj{1}\right)$, return the measurement
result~$1$ with the post-measurement state~$\ket{1}$;
\item With probability~$\mu_{\phi}\left(\proj{0}\right)$, return the measurement
result~$0$ with the post-measurement state~$\ket{0}$;
\item With probability~$\mu_{\phi}\left(\proj{-1}\right)$, return the
measurement result~$x$ with the post-measurement state~$\ket{-1}$.
\end{enumerate}
\item The observable operator~$\mathbf{J}_{z}^{2}=\proj{1}+\proj{-1}$,
and its measurement process~${\cal J}_{z}^{2}$:
\begin{enumerate}
\item With probability~$\mu_{\phi}\left(\proj{1}+\proj{-1}\right)$, return
the measurement result~$1$ with the post-measurement state~$\ket{1}\ip{1}{\phi}+\ket{-1}\ip{-1}{\phi}$;
\item With probability~$\mu_{\phi}\left(\proj{0}\right)$, return the measurement
result~$0$ with the post-measurement state~$\ket{0}$.
\end{enumerate}
\end{itemize}
As an operator, it is clear that $\lim_{x\rightarrow1}\mathbf{O}_{x}=\mathbf{J}_{z}^{2}$,
and we should have $\lim_{x\rightarrow1}{\cal O}_{x}={\cal O}_{1}$
for the measurement process. However, it is not obvious why ${\cal O}_{1}={\cal J}_{z}^{2}$.
Although they have the same probability for the measurement results,
but their post-measurement states are different. This might be a defect
of representing a measurement process as an observable. As $\mathbf{O}_{1}=\mathbf{J}_{z}^{2}$,
there is no observable corresponding to the measurement process~${\cal O}_{1}$.}

>>>>

In the remainder of the paper, we consider variations of quantum
probability spaces motivated by computation of numerical quantities in
a world with limited resources:
\begin{itemize}
\item Instead of the Hilbert space $\Hilb$ (constructed over the
  uncountable and uncomputable complex numbers $\mathbb{C}$), we will
  consider variants constructed over finite
  fields~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013}.
\item Instead of real-valued probability measures producing results in
  the uncountable and uncomputable interval $[0,1]$, we will consider
  finite set-valued probability measures~\cite{PuriRalescu1983}.
\end{itemize}
We will then ask if it is possible to construct variants of quantum
probability spaces under these conditions. The main question is
related to the definition of probability measures: is it possible to
still define a probability measure as a function that depends on a
single state? Specifically,
\begin{itemize}
\item given a state $\ket{\psi}$, is there a probability measure
  mapping events to probabilities that only depends on $\ket{\psi}$?
  In the conventional quantum probability space, the answer is yes by
  the Born rule~\cite{Born1983,Mermin2007} and the map is given by:
  $E \mapsto \ip{\psi}{E\psi}$.
\item given a probability measure $\mu$
  mapping each event $E$
  to a probability, is there a \emph{unique} state $\psi$
  such that $\mu(E)
  =
  \ip{\psi}{E\psi}$? In the conventional case, the answer is yes by
  Gleason's
  theorem~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
\end{itemize}

@@

\item A set of mutually orthogonal projections $P_{i}$ is called an \emph{ideal
measurement} if it is a partition of the identity, i.e.,
$\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$.

@@

\yutsung{About continuity, one of the confusion comes from the subtle
correspondence between the measurement processes and observables.
Consider the following observables and their measurement processes:
\begin{itemize}
\item For any $x\in\mathbb{R}$, consider the observable operator~$\mathbf{O}_{x}=\proj{1}+x\proj{-1}$.
Except $x=1$, given the system in the state~$\ket{\phi}$, we can
denote the measurement process for $\mathbf{O}_{x}$ by ${\cal O}_{x}$:
\begin{enumerate}
\item With probability~$\mu_{\phi}\left(\proj{1}\right)$, return the measurement
result~$1$ with the post-measurement state~$\ket{1}$;
\item With probability~$\mu_{\phi}\left(\proj{0}\right)$, return the measurement
result~$0$ with the post-measurement state~$\ket{0}$;
\item With probability~$\mu_{\phi}\left(\proj{-1}\right)$, return the
measurement result~$x$ with the post-measurement state~$\ket{-1}$.
\end{enumerate}
\item The observable operator~$\mathbf{J}_{z}^{2}=\proj{1}+\proj{-1}$,
and its measurement process~${\cal J}_{z}^{2}$:
\begin{enumerate}
\item With probability~$\mu_{\phi}\left(\proj{1}+\proj{-1}\right)$, return
the measurement result~$1$ with the post-measurement state~$\ket{1}\ip{1}{\phi}+\ket{-1}\ip{-1}{\phi}$;
\item With probability~$\mu_{\phi}\left(\proj{0}\right)$, return the measurement
result~$0$ with the post-measurement state~$\ket{0}$.
\end{enumerate}
\end{itemize}
As an operator, it is clear that $\lim_{x\rightarrow1}\mathbf{O}_{x}=\mathbf{J}_{z}^{2}$,
and we should have $\lim_{x\rightarrow1}{\cal O}_{x}={\cal O}_{1}$
for the measurement process. However, it is not obvious why ${\cal O}_{1}={\cal J}_{z}^{2}$.
Although they have the same probability for the measurement results,
but their post-measurement states are different. This might be a defect
of representing a measurement process as an observable. As $\mathbf{O}_{1}=\mathbf{J}_{z}^{2}$,
there is no observable corresponding to the measurement process~${\cal O}_{1}$.}
